### 2018-05-11 Sections/economics_of_the_quantum_internet.tex
Bib, economics, quantcoin

For polynomial scaling functions,
\begin{align}
f_\text{sc}(n) &= n^{p_\text{sc}},\nonumber\\
f_\text{size}(s) &= s^{p_\text{size}}.
\end{align}
This yields problem size,
\begin{align}
	s &= n^{\frac{1}{p_\text{size}}} \cdot {n_\text{global}}^\frac{p_\text{sc}-1}{p_\text{size}} \nonumber\\
	&= O(\mathrm{poly}(n_\text{global})),
\end{align}
demonstrating polynomial scaling in our solvable problem size against the size of the network.

For exponential scaling functions,
\begin{align}
f_\text{sc}(n) &= e^{\alpha_\text{sc}n},\nonumber\\
f_\text{size}(s) &= e^{\alpha_\text{size}s},
\end{align}
we obtain,
\begin{align}
s &= \log\left(n \frac{e^{\alpha_\text{sc}n_\text{global}}}{\alpha_\text{sc}n_\text{global}}\right) \nonumber\\
&= O(n_\text{global}),
\end{align}
demonstrating that the solvable problem size grows linearly with network size. That is to say, waiting for a doubling in the external network's size will also double the size of a \textbf{BQP}-complete\index{\textbf{BQP}-complete} problem that can be solved in the same time.

@@

	\begin{flushleft}Problem size scaling function (Sec.~\ref{sec:prob_sc_func})\end{flushleft} & \[s = f_\text{size}^{-1}(n\cdot \chi_\text{sc}(n_\text{global}))\] & \[\frac{n}{\alpha_\text{size}}\] & \[n^{\frac{1}{p_\text{size}}} \cdot {n_\text{global}}^\frac{p_\text{sc}-1}{p_\text{size}}\] & \[\alpha_\text{sc}n_\text{global} + \log(n)\]\[-\log(\alpha_\text{sc}n_\text{global})\] \\

>>>>

For polynomial scaling functions,
\begin{align}
f_\text{sc}(n) &= n^{p_\text{sc}},\nonumber\\
f_\text{size}(s) &= s^{p_\text{size}}.
\end{align}
This yields problem size,
\begin{align}
	s &= (n \cdot {n_\text{global}}^{p_\text{sc}-1})^\frac{1}{p_\text{size}} \nonumber\\
	&= O(\mathrm{poly}(n_\text{global})),
\end{align}
demonstrating polynomial scaling in our solvable problem size against the size of the network.

For exponential scaling functions,
\begin{align}
f_\text{sc}(n) &= e^{\alpha_\text{sc}n},\nonumber\\
f_\text{size}(s) &= e^{\alpha_\text{size}s},
\end{align}
we obtain,
\begin{align}
s &= \log\left(n \frac{e^{\alpha_\text{sc}n_\text{global}}}{\alpha_\text{sc}n_\text{global}}\right) \nonumber\\
&= \alpha_\text{sc}n_\text{global} + \log(n)-\log(\alpha_\text{sc}n_\text{global}) \nonumber\\
&= O(n_\text{global}),
\end{align}
demonstrating that the solvable problem size grows linearly with network size. That is to say, waiting for a doubling in the external network's size will also double the size of a \textbf{BQP}-complete\index{\textbf{BQP}-complete} problem that can be solved in the same time.

@@

	\begin{flushleft}Problem size scaling function (Sec.~\ref{sec:prob_sc_func})\end{flushleft} & \[s = f_\text{size}^{-1}(n\cdot \chi_\text{sc}(n_\text{global}))\] & \[\frac{n}{\alpha_\text{size}}\] & \[(n \cdot {n_\text{global}}^{p_\text{sc}-1})^\frac{1}{p_\text{size}}\] & \[\alpha_\text{sc}n_\text{global} + \log(n)\]\[-\log(\alpha_\text{sc}n_\text{global})\] \\

### 2018-05-11 Sections/essay_quantcoin.tex
Bib, economics, quantcoin

%
% QuantCoin - A Computation-Backed Currency]
%

@@

The advent of cryptocurrencies\index{Cryptocurrency} (Sec.~\ref{sec:bitcoin_blockchain}) places the death of fiat currency\index{Fiat currency} firmly on the horizon. Central banks around the world have been consistently inflating and devaluing national currencies, destroying their integrity through loose print-on-demand monetary policies to finance ever-increasing debt.

What makes a sound currency\index{Sound currency}? First of all, it must exhibit scarcity\index{Scarcity} and be difficult or impossible to counterfeit\index{Counterfeit} -- it should not be possible to forge unlimited quantities out of thin air, a quality most certainly not inherent to the fiat currencies maintained by central banks. Second, its abundance and demand should exhibit relative stability and predictability over time, so as to create a stable money supply\index{Money supply} and inflationary rate. For these reasons, gold\index{Gold standard} for thousands of years was accepted as legal tender, since it is naturally scarce and much work must be invested into its production. For the same reasons, emerging cryptocurrencies like BitCoin\index{BitCoin} have become widely adopted and even the norm in hyper-inflating countries like Venezuela where fiat currency has lost all integrity, as they exhibit these same traits. But rather than scarcity of a natural resource, we are dealing with artificial scarcity of bit-strings, cryptographically enforced to satisfy certain mathematical properties that cannot be easily counterfeited.

@@

Existing Blockchain-based cryptocurrencies like Bitcoin\index{Blockchain}\index{Bitcoin} (Sec.~\ref{sec:bitcoin_blockchain}) are actually examples of computation-backed currencies, where the mining process requires brute-force computation of a large number of SHA256\index{SHA256} hash functions\index{Hash functions}. Unfortunately, however, in the case of Bitcoin these computations are wasted, since they are not solving any problems of merit. Rather miners are made to perform them purely for the sake of imposing artificial scarcity. QuantCoin\texttrademark on the other hand backs the currency with real-world computations of value, as determined by market participants at the time, a far better utilisation of computational power, with far greater confidence in its monetary value.

>>>>

%
% QuantCoin - A Computation-Backed Currency
%

@@

The advent of cryptocurrencies\index{Cryptocurrency} (Sec.~\ref{sec:bitcoin_blockchain}) places the death of fiat currency\index{Fiat currency} firmly on the horizon. Central banks around the world have been consistently inflating and devaluing national currencies, destroying their integrity through loose print-on-demand monetary policies to finance ever-increasing debt. National currencies and currency unions sit at the brink of crumbling.

What makes a sound currency\index{Sound currency}? First of all, it must exhibit scarcity\index{Scarcity} and be difficult or impossible to counterfeit\index{Counterfeit} -- it should not be possible to forge unlimited quantities out of thin air, a quality most certainly not inherent to the fiat currencies maintained by central banks. Second, its abundance and demand should exhibit relative stability and predictability over time, so as to create a stable money supply\index{Money supply} and inflationary rate.

For these reasons, gold\index{Gold standard} for thousands of years was accepted as legal tender, since it is naturally scarce and much work must be invested into its production. For the same reasons, emerging cryptocurrencies like BitCoin\index{BitCoin} have become widely adopted and even the norm in hyper-inflating countries like Venezuela where fiat currency has lost all integrity, as the cryptocurrencies exhibit these desired traits. But rather than scarcity of a natural resource, we are dealing with artificial scarcity of bit-strings, cryptographically enforced to satisfy certain mathematical properties that cannot be easily counterfeited.

@@

Existing Blockchain-based cryptocurrencies like Bitcoin\index{Blockchain}\index{Bitcoin} (Sec.~\ref{sec:bitcoin_blockchain}) are actually examples of computation-backed currencies, where the mining process requires brute-force computation of a large number of SHA256\index{SHA256} hash functions\index{Hash functions}, to discover hashes satisfying certain constraints. Unfortunately, however, in the case of Bitcoin these computations are wasted, since they are not solving any problems of merit. Rather miners are made to perform them purely for the sake of imposing artificial scarcity via `proof-of-work'\index{Proof-of-work}\footnote{This proof-of-work notion was originally borrowed from the Hashcash\index{Hashcash} protocol for preventing email spamming.}. QuantCoin\texttrademark on the other hand backs the currency with real-world computations of value, as determined by market participants at the time, a far better utilisation of computational power, with far greater confidence in its objective monetary value.

### 2018-05-11 Sections/physical_architectures_for_quantum_computing.tex
Ent purif
Bib, economics, quantcoin

The quadrature eigenstates\index{Quadrature eigenstates} are mutually related to each other by a Fourier transform\index{Fourier transform},
\begin{align}
\ket{x} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{-2 i x p} \ket{p} \,dp,\nonumber \\
\ket{p} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{+2 i x p} \ket{x} \,dx.
\end{align}

@@

\subsubsection{Encoding quantum information using squeezed state}\index{Squeezed state encoding}

@@

\comment{To do.}

>>>>

The quadrature eigenstates\index{Quadrature eigenstates} are mutually related to each other by a Fourier transform\index{Fourier transform},
\begin{align}
\ket{x} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{-2 i x p} \ket{p} \,dp,\nonumber \\
\ket{p} &= \frac{1}{\sqrt{\pi}} \int_{-\infty} ^\infty e^{2 i x p} \ket{x} \,dx.
\end{align}

@@

\subsubsection{Encoding quantum information using squeezed states}\index{Squeezed state encoding}

@@

\comment{To do: Jon Dowling. Entirely new section, not subsection of another existing section.}

\comment{This is to be an introductory review of this field, starting from the beginning. Use previous sections on KLM and optical cluster states as a guideline for level of detail. The following topics need to be included, and you're at full liberty to throw is as much other material as you think is appropriate to communicate the basic ideas of the approach.}

\comment{* How are qubits defined - both physical and mathematical descriptions.}

\comment{* How is state preparation performed?}

\comment{* How are single- and two-qubit gates implemented?}

\comment{* How is readout (measurement) performed?}

\comment{* Scalability issues - anything important re scaling these architectures up arbitrarily.}

\comment{* What are the dominant error models/mechanisms? (both mathematically and physically)}

\comment{* Current obstacles - what needs to be overcome for this to succeed?}

\comment{* Current state of the art with comprehensive referencing}

\comment{* Anything else you decide is relevant or important}

### 2018-05-11 Sections/the_quantum_space_race.tex
Bib, economics, quantcoin

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{space_1}
\caption{Various possibilities for space-based quantum communication. (a) Satellite-to-satellite quantum communication \cite{bib:byrnes2017lorentz}. (b) Ground-to-satellite quantum communication \cite{bib:armengol08}.}
\label{fig:space_1}
\end{figure*}

@@

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{space_2}
\caption{Satellites employing quantum technologies from various groups across the world: Japan \cite{bib:horiuchi2015view}, Italy \cite{bib:vallone15}, Canada \cite{bib:jennewein2014qeyssat}, Singapore \cite{bib:tang2016generation}, and China \cite{bib:gibney16}.}
\label{fig:space_2}
\end{figure*}

>>>>

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{space_1}
\caption{Various possibilities for space-based quantum communication. (a) Satellite-to-satellite quantum communication \cite{bib:byrnes2017lorentz}. (b) Ground-to-satellite quantum communication \cite{bib:armengol08}. \comment{Tim: do we have figure permission for this?}}
\label{fig:space_1}
\end{figure*}

@@

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{space_2}
\caption{Satellites employing quantum technologies from various groups across the world: Japan \cite{bib:horiuchi2015view}, Italy \cite{bib:vallone15}, Canada \cite{bib:jennewein2014qeyssat}, Singapore \cite{bib:tang2016generation}, and China \cite{bib:gibney16}. \comment{Tim: do we have figure permission for this?}}
\label{fig:space_2}
\end{figure*}
